Characterizing Execution Times on Realistic Programs

### 2018-09-14 pt_characterization/real_data/paper.tex
More changes

\author{
Database \& Big Data Systems Laboratory,\\
School of Computer Science and Engineering, \\
Kyungpook National University,\\
Young-Kyoon Suh\\
}
\maketitle

@@

\subsection{Insertion Sort on {\tt sodb8}~\label{sec:add_new}} 
This section shows a series of histograms of an insertion sorting program that 
sorts the elements of a given array in non-decreasing order. 
The program repeatedly runs 300 times for a given input size. 
The input size for the program 
varies from 100,000 to 1,160,000 integer elements, which are randomly generated. 
Note that each sort program over a specific input size is termed SORT{\it x}: 
for instance, SORT100 indicates the insertion sort program over 100K elements. 
This experiment was performed on {\tt sodb8} \underline{plugged into {\em bottom left}} power strip.

@@

\subsection{One-to-One Comparison between An Insertion Sort \& A Corresponding INC Programs~\label{sec:sort}} 
This section compares program time histograms 
of an insertion sort and a nested-for-loop programs (termed INC) with different input sizes. The insertion sort program sorts the elements of a given array in non-decreasing order.  The program repeatedly runs 300 times for a given input size. The input size for the program varies from 144K to 344K integer elements, which are randomly generated. Note that each sort program over a specific input size is termed SORT{\it x}: for instance, SORT100 indicates the insertion sort program over 100K elements. An INC program's task length is correspondingly determined by the program time of an SORT program. In Figures~\ref{fig:sort1},~\ref{fig:sort2}, and~\ref{fig:sort3} 
we perform a match on an SORT program and its corresponding INC program. 
\underline{{\tt sodb8}} was plugged into \underline{{\em bottom left} power strip} 
while \underline{{\tt sodb10}} plugged into \underline{{\em the upper left} power strip}.

>>>>

\author{
Young-Kyoon Suh,\\
Data \& Knowledge Engineering Laboratory,\\
School of Computer Science and Engineering, \\
Kyungpook National University\\
}
\maketitle

@@

\subsection{Insertion Sort on {\tt sodb8}~\label{sec:add_new}} 
This section shows a series of histograms of an insertion sorting program that 
sorts the elements of a given array in non-decreasing order. 
The program repeatedly runs 300 times for a given input size. 
The input size for the program 
varies from 100,000 to 1,160,000 integer elements, which are randomly generated. 
Note that each sort program over a specific input size is termed SORT{\it x}: 
for instance, SORT100 indicates the insertion sort program over 100K elements. 
%This experiment was performed on {\tt sodb8} \underline{plugged into {\em bottom left}} power strip.

\begin{table}[h]
\begin{center}
\begin{tabular}{|p{4cm}|p{3cm}|p{4cm}|p{4cm}|} \hline
Machine & Task Length & Description & Time Length\\ \hline
{\tt sodb8}  (plugged into the {\em bottom left} power strip) & SORT100 ... SORT2320 & Runs of 300 samples & 2018-03-02 $\sim$2018-03-10\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Detailed description of INC data used for the subsequent histograms\label{tab:exp_notes1}}
\end{table}

@@

\subsection{One-to-One Comparison between An Insertion Sort \& A Corresponding INC Programs~\label{sec:sort}} 
This section compares program time histograms 
of an insertion sort and a nested-for-loop programs (termed INC) with different input sizes. The insertion sort program sorts the elements of a given array in non-decreasing order.  The program repeatedly runs 300 times for a given input size. The input size for the program varies from 144K to 344K integer elements, which are randomly generated. Note that each sort program over a specific input size is termed SORT{\it x}: for instance, SORT100 indicates the insertion sort program over 100K elements. An INC program's task length is correspondingly determined by the program time of an SORT program. In Figures~\ref{fig:sort1},~\ref{fig:sort2}, and~\ref{fig:sort3} 
we perform a match on an SORT program and its corresponding INC program. 
%\underline{{\tt sodb8}} was plugged into \underline{{\em bottom left} power strip} 
%while \underline{{\tt sodb10}} plugged into \underline{{\em the upper left} power strip}.

\begin{table}[h]
\begin{center}
\begin{tabular}{|p{4cm}|p{3cm}|p{4cm}|p{4cm}|} \hline
Machine & Task Length & Description & Time Length\\ \hline
{\tt sodb8}  (plugged into the {\em bottom left} power strip) & SORT144 ... SORT344 & Runs of 300 samples & 2018-03-09 $\sim$2018-03-17\\ \hline
{\tt sodb10}  (plugged into the {\em upper left} power strip) & INC8.8 ... INC51.5 & Runs of 300 samples & 2018-03-18 $\sim$2018-03-18\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Detailed description of INC data used for the subsequent histograms\label{tab:exp_notes2}}
\end{table}
